Parallel Multi-objective Optimization Using Information Framework for Constructing Global Optimization Algorithms

### 2017-07-13 2017/URAL-PDC/u_pdc_paper.tex
u_pdc: change title, add acknowledgments section

\usepackage[english]{babel}
\usepackage{amsmath,amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{tabularx}
\DeclareMathOperator{\sign}{sign}
\newcolumntype{K}[1]{>{\centering\arraybackslash}p{#1}}
%
\begin{document}
%
\mainmatter              % start of the contributions
%
\title{Parallel Multi-objective Optimization on CPU Using Information Framework for
Constructing Global Optimization Algorithms}
%
\titlerunning{Parallel Multi-objective Optimization}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Vladislav V. Sovrasov}
%
\authorrunning{Vladislav V. Sovrasov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Vladislav V. Sovrasov}
%
\institute{State University of Nizhny Novgorod, Nizhny Novgorod, Russia\\
\email{sovrasov.vlad@gmail.com}}

@@

\section{Conclusion}
In the present work, a method for solving the multi-objective optimization problems allowing
finding a uniform estimate of the set of the weakly-optimal points has been considered. The
techniques of parallelization and of the acceleration of convergence common for all algorithms
of similar structure have been applied. The numerical experiments performed have
demonstrated a speedup in convergence when using the local refinement. Also, the
parallelization based on the characteristics was found to be efficient for this method. The
speedup in iterations at the parallelization based on the characteristics appeared to be linear in
most cases as for the information methods of scalar optimization (see the results of the
parallelization of the scalar optimization method, for example, in
\cite{barkalovLebedef2016}). From the results of the experiments, one can conclude that it is
expedient to apply the parallel MOALR in the problems of low dimensionality (1 to 3) with
the computation-costly criteria. Moreover, the property of uniform convergence of the considered
algorithm to the whole set of the weakly-optimal solutions has been demonstrated on the
numerical examples.
%
% ---- Bibliography ----
%
%\bibliographystyle{plain}
%\bibliographystyle{alpha}
\bibliographystyle{unsrt}
%\bibliographystyle{splncs03}
\bibliography{u_pdc_refs}

>>>>

\usepackage[english]{babel}
\usepackage{amsmath,amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{tabularx}
\DeclareMathOperator{\sign}{sign}
\newcolumntype{K}[1]{>{\centering\arraybackslash}p{#1}}
%
\begin{document}
%
\mainmatter              % start of the contributions
%
\title{Parallel Multi-objective Optimization Using Information Framework for
Constructing Global Optimization Algorithms}
%
\titlerunning{Parallel Multi-objective Optimization}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Vladislav V. Sovrasov}
%
\authorrunning{Vladislav V. Sovrasov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Vladislav V. Sovrasov}
%
\institute{State University of Nizhny Novgorod, Nizhny Novgorod, Russia\\
\email{sovrasov.vlad@gmail.com}}

@@

\section{Conclusion}
In the present work, a method for solving the multi-objective optimization problems allowing
finding a uniform estimate of the set of the weakly-optimal points has been considered. The
techniques of parallelization and of the acceleration of convergence common for all algorithms
of similar structure have been applied. The numerical experiments performed have
demonstrated a speedup in convergence when using the local refinement. Also, the
parallelization based on the characteristics was found to be efficient for this method. The
speedup in iterations at the parallelization based on the characteristics appeared to be linear in
most cases as for the information methods of scalar optimization (see the results of the
parallelization of the scalar optimization method, for example, in
\cite{barkalovLebedef2016}). From the results of the experiments, one can conclude that it is
expedient to apply the parallel MOALR in the problems of low dimensionality (1 to 3) with
the computation-costly criteria. Moreover, the property of uniform convergence of the considered
algorithm to the whole set of the weakly-optimal solutions has been demonstrated on the
numerical examples.

\section*{Acknowledgments}
The study was supported by the Russian Science Foundation, project No 16-11-10150.
%
% ---- Bibliography ----
%
\bibliographystyle{splncs03}
\bibliography{u_pdc_refs}
